### 2023-02-02 README.Rmd
Update README
Add GHA

<!-- badges: start -->
<!-- badges: end -->

@@

```{r, include = FALSE}
library(gran)
graph <- readRDS("tests/testdata/graph.RDS")
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/chainsawriot/gran/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/gran/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

```{r, include = FALSE}
devtools::load_all()
graph <- readRDS("tests/testdata/graph.RDS")
```
